Coherent optical association of single molecules

### 2020-08-18 paper.tex
Update on Overleaf.

\begin{document}
\title{Coherent optical association of single molecules}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\author{Kenneth Wang}
\author{Jessie T. Zhang}
\author{Lewis Picard}
\author{William Cairncross}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

\begin{abstract}
  We report coherent association of a single NaCs molecule in an optical tweezer
  through an optical Raman transition.
  By selecting a deeply bound intermediate state,
  we suppress the scattering loss during the transfer process.
  Starting from atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule we create have a zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}.
  We demonstrate that coherent creation of ground state single molecule is possible,
  even without Feshbach resonance or narrow optical transition.
\end{abstract}

@@

Trapped neutral molecules, assembled in an array of optical tweezers,
are a promising platform to study quantum infoqrmation and quantum simulations.

@@

In this Letter, we demostrate that a single ground electronic state molecule can be formed
from two single optical tweezers by driving an optical Raman transition

>>>>

\begin{document}
\title{Coherent optical association of single molecules}
\author{Yichao Yu}
\email{yichaoyu@g.harvard.edu}
\author{Kenneth Wang}
\author{J. D. Hood}
\author{Lewis Picard}
\author{Jessie T. Zhang}
\author{William Cairncross}
\author{Jeremy Hutson}
\author{Till Rosenband}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
  %We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition. 
  This  technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom. 
\end{abstract}

@@

Trapped neutral molecules, assembled in an array of optical tweezers, are a promising platform to study quantum infoqrmation and quantum simulations.
1. we want to have a diverse species to tailor to different applications. 2. but so far all has been done with Feshbach association (before STIRAP), or in the case of Sr2, a narrow excited state. Previous work on near-threshold Raman transfer has been incoherent. (suggested referees: Florian Shreck and Immanual Bloch)

In this Letter, we survey theoretically the best electronic intermediate state, detuning, etc that balance coupling/transfer efficiency and photon scattering to demonstrate coherent association of a electronic ground-state molecule from two atoms. Because the electronic excited state we used are generic in most diatomic molecules, this technique is general....

@@
